Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-07-26 article.rnw
Extract the article preamble into a separate file.
Much of the preamble will be duplicated for the supplementary,
so this prevents code duplication.

\documentclass[12pt,titlepage]{article}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{import}
\usepackage{authblk}

%Images & tables
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{arydshln}

\captionsetup{subrefformat=parens} %Changes only \subref, not \ref.
\let\Subref\subref
%TODO: Make \cref figure out if it should be a subref, and use cref throughout.

%Journal font & paper requirements
\usepackage{newtxtext} %Times New Roman
\usepackage[letterpaper,margin=1in]{geometry}

%Preprint
\usepackage{lineno} \linenumbers
\usepackage{setspace} \doublespacing
\usepackage[nomarkers,tablesfirst,notablist,nofiglist]{endfloat}
\addtodelayedfloat{figure}{\clearpage} %Each delayed figure on a new page.

%Ensure title page is numbered, as journal style requires it.
%Using https://tex.stackexchange.com/a/172005, adapted not to bother with two column stuff.
\makeatletter
\renewenvironment{titlepage}{\thispagestyle{plain}}{\newpage}
\makeatother

%Referencing
\import{reference-styles/}{ecology.tex}
\addbibresource{bibliography/references.bib}
\addbibresource{references.bib}
\usepackage{placeins} %Provides \FloatBarrier

\usepackage{hyperref}
\usepackage{cleveref}

%Title Page
\title{Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
\author{Christopher R.\ P.\ Brown}
\author{Daniel B.\ Stouffer}
\affil{Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
\date{}

<<include=FALSE>>=
	knitr::opts_chunk$set(echo = FALSE) #Never show the code, only output.
	knitr::opts_chunk$set(results = 'asis') #Text is grey without this.
	knit_hooks$set(inline = function(x) {x}) #Disable automatic formatting of in-line material.
@

<<include=FALSE>>=
	library(magrittr)
	load("output/article-data.rda")
@

\newcommand\ic{\Sexpr{ic_name}}

\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\icnum[1]{\num[round-mode=places,round-precision=2]{#1}} %For information criteria.
\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\cornum[1]{\num[round-mode=places,round-precision=3]{#1}}

\newcommand\mantelstat{\ensuremath{r_{\text{M}}}}

\newcommand\keywords[1]{\emph{Key words: #1}}

\pgfplotsset{%
	colormap={coclassification}{color=(white) color=(red)}
}
\colorlet{coclassification diagonal}{black!20}

>>>>

\documentclass[12pt,titlepage]{article}

<<preamble,child="preamble.rnw">>=
@
